---
title: "Schedule"
page-layout: full
css: layout/css/adveconpol.scss
---

```{r packages, include=FALSE, cache=FALSE}
library(tidyverse)
library(readxl)
library(glue)
library(knitr)
library(kableExtra)

Sys.setlocale(locale="en_US.UTF-8")
schedule <- read_xlsx(here::here("data/schedule/schedule.xlsx"))
```

In this table you find the dates and contents of all classes.


::: {.schedule-table}
```{r table, echo=F, results='asis'}
schedule %>% arrange(Date) %>% select(-c(Chart)) %>%
  mutate(Slides = ifelse(!is.na(Slides),
        glue('<a href="slides/{Slides}/" target = "_blank">
             <i class="fa-solid fa-display fa-lg"></i></a>'),
        glue('<font color="#e9ecef"><i class="fa-solid fa-display fa-lg"></i></font>')), 
        Code = ifelse(!is.na(Code),
        glue('<a href="data/code/{Code}" target = "_blank">
             <i class="fa-solid fa-code fa-lg"></i></a>'),
        glue('<font color="#e9ecef"><i class="fa-solid fa-code fa-lg"></i></font>')),
        Assignment = ifelse(!is.na(Assignment),
        glue('<a href="#h{Assignment}"><i class="fa-solid fa-pen fa-lg"></i></a>'),
        glue('<font color="#e9ecef"><i class="fa-solid fa-pen fa-lg"></i></font>')),
        Date = format(Date, '%b %d, %Y')) %>%
  kbl(escape = FALSE, align = "ccclcc", table.attr = 'class="schedule-table"') %>% 
  kable_styling() %>% 
  column_spec(1:3, width = "12%") %>% 
  column_spec(4, width = "34%") %>% 
  column_spec(5:7, width = "10%")
```
:::

#### Assignments

Assignment [[1]](#h1) provides the setup of the R infrastructure that is required in this course. There are no points for this assignment. Assignments [[2]](#h2) to [[4]](#h4) are recreations of examplary figures provided below. These examples are related to figures that are discussed in class. Students should then try to reproduce the plots at home and improve their individual coding skills. The raw data for the figures are available as `*.csv` files below.  

##### Homework 1{#h1}

```{r assign1, include = F}
assignvars <- schedule %>% filter(!is.na(Assignment)) %>%
  mutate(deadline = format(Date, '%B %d, %Y'),
         data = paste0("data/assignments/", Chart, ".csv"),
         png = paste0("data/assignments/", Chart, ".png"))
```

::: {.columns}
::: {.column width="20%"}
[![](`r assignvars$png[[1]]`)](`r assignvars$png[[1]]`)
:::

::: {.column width="3%"}
:::

::: {.column width="70%"}
1. Install the latest [R version (v4.2.2)](https://cran.r-project.org/)

2. Install the latest version of [RStudio Desktop](https://posit.co/download/rstudio-desktop/)

3. Open RStudio, copy the following code into the console and execute:
`install.packages(c("tidyverse", "rmarkdown", "scales", "lubridate", "colorspace", "devtools")); sessionInfo()`

4. Click on `Help > About RStudio`

5. Make sure that both the R version (Console) and the RStudio version are visible, take a screenshot and upload it to the [learning platform](https://learn.wu.ac.at) before `r assignvars$deadline[[1]]` at 9 a.m.
:::
:::

##### Homework 2{#h2}

::: {.columns}
::: {.column width="20%"}
[![](`r assignvars$png[[2]]`)](`r assignvars$png[[2]]`)
:::

::: {.column width="3%"}
:::

::: {.column width="70%"}
Please submit your chart before `r assignvars$deadline[[2]]` at 9 a.m. The data for this assignment is available here: <a href = "`r assignvars$data[[2]]`">{{< fa file-csv >}}</a>
:::
:::

##### Homework 3{#h3}

::: {.columns}
::: {.column width="20%"}
[![](`r assignvars$png[[3]]`)](`r assignvars$png[[3]]`)
:::

::: {.column width="3%"}
:::

::: {.column width="70%"}
Please submit your chart before `r assignvars$deadline[[3]]` at 9 a.m. The data for this assignment is available here: <a href = "`r assignvars$data[[3]]`">{{< fa file-csv >}}</a>
:::
:::

##### Homework 4{#h4}

::: {.columns}
::: {.column width="20%"}
[![](`r assignvars$png[[4]]`)](`r assignvars$png[[4]]`)
:::

::: {.column width="3%"}
:::

::: {.column width="70%"}
Please submit your chart before `r assignvars$deadline[[4]]` at 9 a.m. The data for this assignment is available here: <a href = "`r assignvars$data[[4]]`">{{< fa file-csv >}}</a>
:::
:::